Target Markdown

### 2022-10-12 _targets.Rmd
rozbite targets ale updatovana pipelina

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path, nrows = 20),
              format = "qs"),
     tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
      tar_target(ids_complete, create_ids_complete(ids, db_path),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete))#,

    # tar_target(all_pubs,
    #        get_all_pubs(db_path, ids_complete), 
    #           format = "qs"),
    # tar_target(one_author,
    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
    #           format = "qs", pattern = map(ids_complete_vector), iteration = "list")
    # 
)
```

@@

     tar_target(matching, match(db_path, ids),
                format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, matching, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
              format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list")

@@

   tar_target(topic_model_input,
              make_topic_model_input(all_pubs)) #,

    # tar_target(topic_number,
    #           find_topic_number(topic_model_input),
    #             format = "qs") #, 
    # tar_target(topic_model,
    #            make_topic_model(topic_model_input),
    #             format = "qs")

@@

    tar_target(edgelist,
               make_edgelist(one_author),
                format = "qs", pattern = map(one_author), iteration = "list"),
    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")

@@

    tar_target(eigen_centr,
               calc_eigen_centr(graph, ids_complete, one_author, db_path),
               format = "qs", pattern = map(graph, one_author), iteration = "list")

@@

     tar_target(clustering,
                calc_clustering(graph, ids_complete, one_author, db_path),
               format = "qs", pattern = map(graph, one_author), iteration = "list") 
    #            
    # 
)

@@

     tar_target(ind_pubs,
                calc_ind_pubs(one_author, ids_complete, db_path), 
                format = "qs", pattern = map(one_author),                  iteration = "list")

@@

     tar_target(ind_topics,
                calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
                format = "qs", pattern = map(one_author), iteration = "list")

@@

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
               format = "qs") #,
     # tar_target(testing,
     #           just_test(db_path),
     #           format = "qs")

>>>>

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path),
              format = "qs"),
     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path), format = "qs"),
     # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
     #          format = "qs"),
      tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
      tar_target(ids_complete, create_ids_complete(ids, db_path),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete))

    # tar_target(all_pubs,
    #        get_all_pubs(db_path, ids_complete), 
    #           format = "qs"),
    # tar_target(one_author,
    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
    #           format = "qs")
    # 
)
```

@@

     # tar_target(matching, match(db_path, ids, gender),
     #            format = "qs"),
     # tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
     # tar_target(sup_control, read.csv2(sup_path),
     #          format = "qs"),
     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
     #          format = "qs"),
     # tar_target(final_data, refine_data(matching, db_path, ids, sup_control),
     #            format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     # tar_target(ids_full_vector,
     #           make_ids_full_vector(matching)),
    #  tar_target(all_pubs,
    #        get_all_pubs(db_path, matching, ids_complete), 
    #           format = "qs"),
    # tar_target(all_authors,
    #        read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
    #           format = "qs")

@@

   # tar_target(topic_model_input,
   #            make_topic_model_input(all_pubs)) #,
   #                            
   #  # tar_target(topic_number,
   #  #           find_topic_number(topic_model_input),
   #  #             format = "qs") #, 
   #  # tar_target(topic_model,
   #  #            make_topic_model(topic_model_input),
   #  #             format = "qs")

@@

    # tar_target(edgelist,
    #            make_edgelist(one_author),
    #             format = "qs", pattern = map(one_author), iteration = "list"),
    # tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")

@@

    # tar_target(eigen_centr,
    #            calc_eigen_centr(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list")
    # 
)

@@

    #  tar_target(clustering,
    #             calc_clustering(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list") 
    # #            
    # # 
)

@@

     # tar_target(ind_pubs,
     #            calc_ind_pubs(one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author),                  iteration = "list")
     # 
)

@@

     # tar_target(ind_topics,
     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author), iteration = "list")
     # 
)

@@

    # tar_target(final_data,
    #            calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
    #            format = "qs") #,
    #  # tar_target(testing,
    #  #           just_test(db_path),
    #  #           format = "qs")
    # 
)
